Assignment 5

### 2015-02-23 rmtw/a5/latex8.tex
john = fag

\SubSection{Research Question(s)}
One clear main research question
RQ 1 - In which situations should companies expect MDD to be successfully adopted?

>>>>

\SubSection{Research Question(s)}
One clear main research question
RQ 1 - In which situations should companies expect MDD to be successfully adopted?
RQ1 alt: In which situations should companies expect that the adoption of MDD would lead to a performance boost?

RQ 1.1:
In which domain(s) has MDSD been the most successful?

RQ 1.2:
Which software development process has been most successfully used in conjunction with MDSD?

RQ 1.3:
What are the characteristics of systems where MDSD has been successfully implemented?
